---
title: "U.S. Caribbean NCRMP Species for SEDAR "
author: "[Jeremiah Blondeau](https://github.com/jeremiaheb)"
date: "`r format(Sys.time(), '%d %B %Y')`"
mail: "jblondeau@gmail.com"
github: "https://github.com/jeremiaheb/SEDAR_Data_Triage"
logo: "noaa_logo.png"
output:
  ProjectTemplates::Personal:
    toc: TRUE
    number_sections: FALSE
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Needed Libraries
library(rvc)
library(tidyverse)
library(DT)
library(readxl)
library(downloadthis)

# Source Plotting Functions
source('../code/Triage_Outputs.R', local = knitr::knit_global())

# Read in data sets
prico <- readRDS("../data/prico_2001_2023_calibrated.rds")
sttstj <- readRDS("../data/sttstj_2001_2023_calibrated.rds")
stx <- readRDS("../data/stx_2001_2023_calibrated.rds")
```

# **Puerto Rico**

## Species

These species meet the following criteria

1)  Have a calibration factor
2)  Have at least 1% occurrence in any of the NCRMP sampling years 2016 - present

<br>

```{r echo=FALSE}

initial_prico_list <- read_xlsx("../data/island based FMP Stocks list.xlsx", sheet = "PRICO")

table  <- SEDAR_triage_occurrence(df = prico, spp_list = initial_prico_list)

datatable(table, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Species Code", "Family Name", "Scientific Name", "Common Name"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))
```

## Survey Estimates

```{r echo=FALSE}

metric_outputs <- SEDAR_triage_output(prico, table$SPECIES_CD) %>% 
  select(YEAR, SPECIES_CD, REGION, n, density, density_CV, occurrence, occurrence_CV, num_observations)

datatable(metric_outputs, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Year", "Species Code", "Region", "Sample Number", "Density", "Denstiy CV", "Occurrence", "Occurrence CV", "Number of Observations"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))

download_this(metric_outputs,
              output_name = "PRICO_SurveyEstimates",
              output_extension = ".xlsx",
              button_label = "Download data as xlsx",
              button_type = "default",
              has_icon = TRUE,
              icon = "fa fa-save")
```

# **St. Thomas and St. John**

## Species

These species meet the following criteria

1)  Have a calibration factor
2)  Have at least 1% occurrence in any of the NCRMP sampling years 2016 - present

<br>

```{r echo=FALSE}

initial_sttstj_list <- read_xlsx("../data/island based FMP Stocks list.xlsx", sheet = "STTSTJ")

table  <- SEDAR_triage_occurrence(df = sttstj, spp_list = initial_sttstj_list)

datatable(table, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Species Code", "Family Name", "Scientific Name", "Common Name"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))
```

## Survey Estimates

```{r echo=FALSE}

metric_outputs <- SEDAR_triage_output(sttstj, table$SPECIES_CD) %>% 
  select(YEAR, SPECIES_CD, REGION, n, density, density_CV, occurrence, occurrence_CV, num_observations)

datatable(metric_outputs, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Year", "Species Code", "Region", "Sample Number", "Density", "Denstiy CV", "Occurrence", "Occurrence CV", "Number of Observations"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))

download_this(metric_outputs,
              output_name = "STTSTJ_SurveyEstimates",
              output_extension = ".xlsx",
              button_label = "Download data as xlsx",
              button_type = "default",
              has_icon = TRUE,
              icon = "fa fa-save")
```

# **St. Croix**

## Species

These species meet the following criteria

1)  Have a calibration factor
2)  Have at least 1% occurrence in any of the NCRMP sampling years 2016 - present

<br>

```{r echo=FALSE}

initial_stx_list <- read_xlsx("../data/island based FMP Stocks list.xlsx", sheet = "STX")

table  <- SEDAR_triage_occurrence(df = stx, spp_list = initial_stx_list)

datatable(table, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Species Code", "Family Name", "Scientific Name", "Common Name"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))
```

## Survey Estimates

```{r echo=FALSE}

metric_outputs <- SEDAR_triage_output(stx, table$SPECIES_CD) %>% 
  select(YEAR, SPECIES_CD, REGION, n, density, density_CV, occurrence, occurrence_CV, num_observations)

datatable(metric_outputs, 
          class = "cell-border stripe", 
          rownames = FALSE,
          colnames = c("Year", "Species Code", "Region", "Sample Number", "Density", "Denstiy CV", "Occurrence", "Occurrence CV", "Number of Observations"),
          options = list(
            columnDefs = list(list(className = 'dt-center', targets = "_all")),
            info = FALSE,
            paging = TRUE,
            searching = TRUE
          ))

download_this(metric_outputs,
              output_name = "STX_SurveyEstimates",
              output_extension = ".xlsx",
              button_label = "Download data as xlsx",
              button_type = "default",
              has_icon = TRUE,
              icon = "fa fa-save")
```
